\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
I don't like latex citations

\subsection{Scientifical point of view}
Using gamification as a motivational factor isn‘t new, there are several systems and successful gamifications like $"Foursquare"$ \footnote{\url{https://foursquare.com/about/}} on the market. See \ref{sect:star} for a list of other systems using gamification in a health-related environment. The modern health care system is scientifically interesting because it combines several well-known approaches into a new interconnected system and it is unknown if and how such a system can work. There is a high scientific potential in our idea because it combines many of already given approaches with existing infrastructure and organizations. The modern health care system is on the one hand a psychological study on how gamification of everydays tasks can influence peoples behaviour, on the other hand it tries to gather new knowledge in the field of ubiquitous computing, usability and security/privacy. There are several questions we try to answer, see \ref{sect:goals} for an exhaustive list.

>>>>

\subsection{Scientifical point of view}
Using gamification as a motivational factor isn‘t new, there are several systems and successful gamifications like $"Foursquare"$ \footnote{\url{https://foursquare.com/about/}} on the market. See section \ref{sect:star} for a list of other systems using gamification in a health-related environment. The modern health care system is scientifically interesting because it combines several well-known approaches into a new interconnected system and it is unknown if and how such a system can work. There is a high scientific potential in our idea because it combines many of already given approaches with existing infrastructure and organizations. The modern health care system is on the one hand a psychological study on how gamification of everydays tasks can influence peoples behaviour, on the other hand it tries to gather new knowledge in the field of ubiquitous computing, usability and security/privacy. There are several questions we try to answer, see section \ref{sect:goals} for an exhaustive list. \\
